Test of Adaptable User Interfaces

### 2015-07-07 paper.tex
Adding some corrections to Introduction

% =============================================================================
\section{Introduction}
% =============================================================================
Nowadays, with the rise of mobile devices such as notebooks, smartphones, smartwatches and tablets, we have computer systems running everywhere and in different \textit{contexts of use}, which involves three factors: the \textit{platform}, \textit{environment} and \textit{the user}~\cite{ui-eric-plasticity-vs-responsive}. These factors affect the interaction between the user and the system. This interaction happens through the \textit{user interface} (UI) and users have to deal with different UIs adapted to several contexts. Hence the term \textit{adaptable user interfaces}. All this allows us to see that today developing UIs can be as complex as developing the core of the system. There are several questions to be considered, among them: quality. \textit{Software Testing} is one of the most used ways in the industry to assure quality~\cite{test-hdr-lydie}. It can be defined as a process, or a series of processes, designed to ensure computer code does what it was designed to do and, conversely, that it does not anything unintended~\cite{test-art-of-testing}. What is the impact of adaptable user interfaces in software testing? Are there tools ready to test these adaptable UIs?

Answering these questions motivates the development of this project. In this work, we focus on the scenario of having different UIs for the same system. These UIs can be adapted to different devices or have different versions for the same device. For instance, we used as case study, a smart home energy management system prototype with four equivalent versions: three for web and one for mobile environment. This exposes the problem in which we focus: the repetitive work of writing test scripts for different versions of the UIs of the same system.

>>>>

% =============================================================================
\section{Introduction}
% =============================================================================
Nowadays, with the rise of mobile devices such as notebooks, smartphones, smartwatches and tablets, there is computer systems running everywhere and in different \textit{contexts of use}, which involves three factors: the \textit{platform}, \textit{environment} and \textit{the user}~\cite{ui-eric-plasticity-vs-responsive}. These factors affect the interaction between the user and the system. This interaction happens through the \textit{user interface} (UI), and users have to deal with different UIs adapted to several contexts. Hence the term \textit{adaptable user interfaces}. All this allows to see that today developing UIs can be as complex as developing the core of the system. There are several questions to be considered, among them: quality. \textit{Software Testing} is one of the most used ways in the industry to assure quality~\cite{test-hdr-lydie}. It can be defined as a process, or a series of processes, designed to ensure computer code does what it was designed to do and, conversely, that it does not anything unintended~\cite{test-art-of-testing}. What is the impact of adaptable user interfaces on software testing? Are there already tools to test these adaptable UIs?

Answering these questions motivates the development of this project. In this work, we focus on the scenario of having different UIs for the same system. These UIs can be adapted to different devices or have different versions for the same device. For instance, we used as case study a smart home energy management system prototype with four equivalent versions: three for web and one for mobile environment. This exposes the problem which we focus: the repetitive work of writing and maintain test scripts for different versions of the UIs of the same system.
